Full-core analysis of thorium-fueled Molten Salt Breeder Reactor using the SERPENT 2 Monte Carlo code

### 2017-10-23 full-core_msbr_model.tex

The fuel temperature coefficient (FTC) is negative due to thermal Doppler 
broadening of the resonance capture cross sections in the thorium and is in a 
good agreement with early research 
\cite{robertson_conceptual_1971,park_whole_2015}. The moderator temperature 
coefficient is positive due to changing density and would increase during 
reactor operation because of spectrum hardening along with fuel depletion 
\cite{park_whole_2015}. Finally, the total temperature coefficient of 
reactivity is relatively large and negative, despite graphite components, and 
affords excellent reactor stability and controllability.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
We performed \gls{MSBR} full-core analysis using the Serpent 2 Monte Carlo 
code. The complex geometry of the reactor is reconstructed in three-dimensional 
space without any major approximations. Accurate material data was employed to 
calculate reactor key design parameters. The effective multiplication factor 
for initial fuel composition is slightly higher than 1 (1.00389) which allows 
reactor operation from startup to the first online reprocessing cycle. The 
neutron flux energy spectrum was calculated for the whole core and represents 
the epithermal spectrum of the MSBR. The total temperature coefficient is 
negative, consequently, the MSBR has negative temperature feedback, but MTC is 
negative which has a negligible effect on safety because it is outweighed by 
the strong, negative FTC.

>>>>

The fuel temperature coefficient (FTC) is negative due to thermal Doppler 
broadening of the resonance capture cross sections in the thorium and is in a 
good agreement with early research 
\cite{robertson_conceptual_1971,park_whole_2015}. The moderator temperature 
coefficient is positive due to changing density and would increase during 
reactor operation because of spectrum hardening along with fuel depletion 
\cite{park_whole_2015}. Finally, the total temperature coefficient of 
reactivity is relatively large and negative, despite graphite components, and 
affords excellent reactor stability and controllability.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
We performed \gls{MSBR} full-core analysis using the Serpent 2 Monte Carlo 
code. The complex geometry of the reactor is reconstructed in three-dimensional 
space without any major approximations. Accurate material data was employed to 
calculate reactor key design parameters. The effective multiplication factor 
for initial fuel composition is slightly higher than 1 (1.00389) which allows 
reactor operation from startup to the first online reprocessing cycle. The 
neutron flux energy spectrum was calculated for the whole core and represents 
the epithermal spectrum of the MSBR. The total temperature coefficient is 
negative, consequently, the MSBR has negative temperature feedback, but MTC is 
positive which has a negligible effect on safety because it is outweighed by 
the strong, negative FTC.
